Co-citations in context

### 2019-06-12 cocit_r.tex
edited first paragraph page 6

\subsection{Model Misspecification and the Attributes of Disciplinary Context} A source of misspecification in the Uzzi {\em et al.}~model arises from not accounting for disciplinary heterogeneity by treating all references as equiprobable substituents. Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline. If the model approximated citation practice, the proportion of references within papers published in a given discipline $D$ would be expected to be equal to the proportion of articles in the discipline $D$, and--conversely--the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.

We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).

To study the disciplinary composition of references in our custom datasets, we used the the WoS extended classification consisting of 153 subjects aggregated into the five major research areas of life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities. We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions: (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%). We then matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively. We analyzed the composition of the references in our three datasets and observed that 84.2\% of the references in the applied physics dataset belonged to physical sciences, and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area. These data suggest at a high level (i) that applying a discipline-indifferent model in Monte Carlo simulations would result in misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas. Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.

\textcolor{blue}{I don't think the paragraph above makes the point that the distribution that is observed is inconsistent with the Uzzi et al. model. But to make that point, it would be nice to know the proportion of publications in each of the five major subject areas. With that information,  I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.}

>>>>

\subsection{Model Misspecification and the Attributes of Disciplinary Context} A source of misspecification in the Uzzi {\em et al.}~model arises from not accounting for disciplinary heterogeneity by treating all references as equiprobable substituents. Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline. 
If the Uzzi {\em et al.} model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be equal to the proportion of references in  $D$, and--conversely--the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.

%We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).

To study the disciplinary composition of references in our custom datasets, we used the the WoS extended classification consisting of 153 subjects aggregated into the five major research areas of life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities. 
%We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions (some publications qualify for more than one label): (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%). We then matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively. We analyzed the composition of the references in our three datasets and observed that 84.2\% of the references in the applied physics dataset belonged to physical sciences, and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area. 
The two largest of these research areas are physical sciences and life sciences and biomedicine,  which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest.
%While there is some variability in different years, %approximately 35.1\% of the references in WoS are from the physical sciences and approximately 62.8\% of the references are from the life sciences and biomedicine.
While there is some variability over the years, according to the Uzzi  {\em et al.} model, we would expect close to 35.1\% of the references cited by the publications in any large network  to be drawn from the physical sciences and roughly 62.8\% of the references to be drawn from the life sciences and biomedicine.
Yet the empirical data present a very different  story: 79.6\% of the references cited in physical sciences publications are from the physical sciences and 89.9\% of the references cited in life sciences and biomedicine publications are from the life sciences and biomedicine.
In other words, the empirical data shows a strong tendency of publications to cite papers that are in the same major research area rather than in some other research area.  Thus, there is a strong bias towards citations that are {\em inside-the-network} rather than {\em outside-the-network}.
This is inconsistent with the Uzzi {\em et al.} model, but makes sense, given what is well established about citation practice.
%These data suggest at a high level (i) that applying a discipline-indifferent model in Monte Carlo simulations would result in misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas. 
For example, our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, even though that percentage varied among disciplines in the eight specialties they investigated (from approximately 39\% to 89\% for 2006). 
Furthermore, these findings strongly argue that Uzzi {\em et al.}'s model has substantial model misspecification (in deviating substantially from the empirical data), and supports our concern that
definitions of  innovation and conventionality that are based on deviation from expected values under Uzzi's model may not be merited.

%\textcolor{blue}{I don't think the paragraph above makes the point that the distribution that is observed is inconsistent with the Uzzi et al. model. But to make that point, it would be nice to know the proportion of publications in each of the five major subject areas. With that information,  I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.}
